\documentclass{article}
\usepackage{hyperref}
\usepackage[margin=15mm]{geometry}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}
\urlstyle{same}

\author{Kadoi Takemaru}

\begin{document}

\section*{Education}
    \subsection*{The University of Tokyo, April 2019 - Present}
        Bachelaor in Information Communication, Department of Engineering
    \subsection*{The University of Tokyo, April 2017 - March 2019}
        Liberal Arts, College of Arts and Sciences

\section*{Projects}
    \subsection*{Language Processor}
        \url{https://github.com/diohabara/languages/blob/master/dcc/}
        \\ C compiler for x86-64.

    \subsection*{Firefox}
        \url{https://slides.com/diohabara/deck}
        \\ I have added additional bookmark properties to Firefox as a hobby.

\section*{Technical Strengths}
    \subsection*{Programming Languages}
        \begin{itemize}
            \item Lisp: can make Lisp itself
            \item Python: can automate mundane things
            \item C: can make C itself
            \item C++: can write alrogithms
            \item Rust: can make Unix-like commands
        \end{itemize}
    \subsection*{CS Backgrounds}
        \begin{itemize}
            \item Computer Architecture
            \item Programming Language thoery
            \item Operating system
            \item other stuff
        \end{itemize}

\section*{Work Experience}
    \subsection*{Wantedly, August 2019 - September 2019, Back-end Engineer}
        \begin{itemize}
            \item \url{https://wantedlyinc.com/ja}
            \item As a software engineer intern, I was working at the web back-end engineering department.
            \item I Improved the Existing functions of its HR application and added new functionalities.
        \end{itemize}

    \subsection*{FLYWHEEL, July 2020 - August 2020, Back-end Engineer}
        \begin{itemize}
            \item \url{https://www.flywheel.jp/}
            \item As a software engineer intern, I was making at the data platform engineering department.
            \item I was making a real-time layer of its data platform.
        \end{itemize}

    \subsection*{Mercari, August 2020 - September 2020, Back-end Engineer}
        \begin{itemize}
            \item \url{https://about.mercari.com/en/}
            \item As a software intern, I was making a static analysis tool for the Go programming language.
        \end{itemize}

    \subsection*{HERP, October 2020 - Present, Back-end Engineer}
        \begin{itemize}
            \item \url{https://herp.co.jp/}
            \item As a software engineer intern, I am making an HR product using Haskell.
        \end{itemize}

\subsection*{Language Skills}
    \begin{itemize}
        \item 2017/8 IELTS L7.5 R8.0 W6.0 S5.5 OA7.0
        \item 2018/1 EIKEN Grade 1
        \item 2018/9 TOEFL iBT R27 L20 S19 W23 Total89
    \end{itemize}

\end{document}
